\documentclass{article}
\usepackage{amsmath, amsfonts, amsthm, geometry, mathtools}

\geometry{
a4paper,
total={8.5in,12in},
left=.5in,
right=.5in,
top=.3in,
bottom=1in,
}

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}}
\title{
    \normalfont \normalsize
    \textsc{Archiver Notes} 
    \horrule{0.5pt} \\
    \huge Introduction to Algorithm \\
    \small Part I: Chapter 1\\
    \horrule{2pt} \\
}

\author{Entropy Archive}
\date{\normalsize 29 April 2015} 
\begin{document}
\maketitle
\section*{Chapter 1}
Basic definition of what an algorithm does, examples of their use and one that
are covered within the confines of the book. They define a correct algorithm is
said to be correct if it halts with correct output. An interesting note about
incorrect algorithms being useful. An example is presented in chapter 31.
Parallelism , a subject that particularly interests, will be covered in chapter
27. Hopefully I get there by the end of the summer.\\ 

\textit{Question from 1.1}
\begin{description}
\item[1.1-1] 
A real world example of 'convex hull' would be useful for automatically created
maps that contain all desired locations. 
\item[1.1-2]
In the real world, complexity to implement an algorithm is always an issue. In
battery powered devices, optimization for battery usage may be more desirable
rather than speed.   
\item[1.1-3] A singularly linked list only points to the next item in the list.
A doubly linked list points to the next item and previous item.The doubly can
move forward and backwards but requires more memory to store the extra pointer.
\item[1.1-4] The traveling-salesman and shortest path are not the same problem.
Both aim to minimize distances, but the distance they are attempting to
minimize are not the same. The traveling-salesman is creating a minimal
distance of a loop that visits each node exactly once. This problem is NP hard.
The shortest path is minimization of distance between two points. This is
solvable problem. 
\item[1.1-5] Compilers want to both compile and optimize code. To do this, they
require both efficient and correct algorithms. Outputting incorrect code that
does not follow standards is unacceptable. If a compiler produce slow code,
customers would not be happy. To keep a completive, they must produce both
correct and efficient code. Quick scrips to complete a simple task such
scraping a websites for information doesn't need to have efficient code. They
are usually 'good' enough if they perform the task quick enough.    
\end{description}

Despite advance in technologies, often the efficiency of an algorithm can be as
important as hardware used. Even in applications that do not require
algorithms, they rely on them. Often Algorithms are technology hidden in
libraries that make these 'simple' program possible. 

\textit{Question 1.2-1}
\begin{description}
\item[1.2-1]
Often you want a graphical interface for an application. If you wish to do
simple gui, a library can be called that will render that data and gather
input. The underlying code to display this gui uses   
\item[1.2-2]
Insertion sort beat merge sort when n inputs are greater than 2 and less than
seven. 
\item[1.2-3] 
Never?
\end{description}
There is only one problem for chapter 1. It essentially ask to calculate
various function. To do this I need to do some research on approximations for
solving for n!, nlg(g).
\begin{table}
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|c|c|}
\hline
 & 1 second & 1 minute & 1 hour & 1 day & 1 month & 1 year & 1 century \\ \hline \hline 
$lg\:n$     & $2^{10^6}$ & $2^{6*10^7}$ & $2^{36*10^7}$ & $2^{864*10^7}$ &
$2^{26784*10^7}$ & $2^{31536*10^8}$ & $2^{31536*10^9}$ \\ \hline 
$\sqrt{n}$  & $10^{12}$ & $3.6*10^{15}$ &  $1.2*10^{19}$ & $7.4*10^{21}$ &
$7 .1*10^{24}$ &  $9.9*10^{26}$ & $9.9*10^{28}$ \\ \hline 
$n$         & $10^{6}$ &  $6*10^{7}$ & $3.6*10^{8}$ &  $8.64*10^{9}$ &
$2.7*10^{11}$ &  $3.15*10^{12}$ & $3.15*10^{13}$  \\ \hline 
$n\:lg\:n$  & & & & & & & \\ \hline 
$n^2$       &  $10^3$ & $7745$ & $60000$ & $293938$ & $1636581$ & $5615692$ &
$17758378$ \\ \hline 
$n^3$       & $100$ & $391$ & $1533$ & $4421$ & $13888$ & $31594$ & $68067$ \\ \hline 
$2^n$       & $19$ & $25$ & $31$ & $36$ & $41$ &  $44$ & $48$ \\ \hline 
$n!$        & & & & & & & \\ \hline 
\end{tabular}
\end{center}
\end{table}

\section*{Chapter 2}
\end{document}

